\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fancyhdr}

\setlength{\headheight}{15pt}
\pagestyle{fancy}
\fancyhf{}
\rhead{Computer Workshop Course}
\lhead{Final Assignment}
\rfoot{Page \thepage}

\title{
    \vspace{2in}
    \textbf{Final CW projrct :}\\
    \textbf{Integration of Tools and Practices}\\
    \large Iran University of Science and Technology\\
    \vspace{2in}
}

\author{
    \vspace{0.5in}
    Koosha Majlessi\\
    Computer Workshop\\
    \vspace{0.5in}
}

\begin{document}

\begin{titlepage}
    \maketitle
    \thispagestyle{empty}
\end{titlepage}

\newpage

\section{Git and GitHub}
\subsection{Repository Initialization and Commits}
First, we go to the GitHub website, click on the "New" option to create a new repository, and then use the terminal to clone it with the git clone command.

\subsection{GitHub Actions for LaTeX Compilation}
First, we create the main.yml file, commit it to GitHub and tag the commit.


\section{Exploration Tasks}
\subsection{Vim Advanced Features}
1. Jump Quickly Between Parentheses
If you're working with code that has lots of parentheses, brackets, or braces, you can jump between them using the precent sign.

2. Change Text Inside Parentheses or Quotes
With the ci command, you can quickly delete and replace text inside parentheses, quotes, or similar structures

3. Vim's Hidden Game!
Vim has a hidden game called Vim Adventure to help you practice commands. Type :help! to access it and explore while learning Vim.
\subsection{Memory profiling}
This semester, you got to know about dynamic memory allocation in C in your Programming Fundamentals class.

\subsubsection{Memory Leak}
A memory leak happens when a program allocates memory but doesn't free it, causing unused memory to remain reserved. It can occur if you forget to call free(), lose the reference to allocated memory, or don't handle errors properly. This leads to wasted memory and can slow down or crash the program.
\subsubsection{Memory profilers}
Valgrind is a tool used for detecting memory leaks, invalid memory accesses, and other memory-related issues in programs. It tracks memory allocations and deallocations, reporting any memory that was allocated but not freed. This helps developers identify and fix memory leaks, improving program reliability and performance.

\subsection{GNU/Linux Bash Scripting}
In this section, you will get to know some handy bash utilities.

\subsubsection{fzf}
Read about a handy CLI tool called \textit{fzf} and answer the following questions:

\begin{itemize}
    \item Fuzzy searching finds matches even with small differences or typos in the search term. It helps locate items by showing similar results, even if the search query is incomplete or misspelled.
    \item The command ls | fzf lists the files and directories in the current directory (ls), then passes that list through a pipe (|) to fzf, which performs fuzzy searching.
        \texttt{ls | fzf}
\end{itemize}

\subsubsection{Using fzf to find your favorite PDF}
You might have came across moments when you want to open up a certain PDF when studying for your final exams but finding the directory of that
PDF is a very gruesome and tiring process. In this section, we will be using \textit{fzf} to find our PDF in seconds! We will be going step by step
on how to find your file and use fzf to select it.

\begin{enumerate}
    \item We first need to list the directory of all the files with the extension \texttt{.PDF}. Write a command to list the directory of all the files with the extension \texttt{.PDF} \\
        \textbf{HINT:} use the command \texttt{fd} for this purpose.
    \item Now we have to select the PDF we want using \textit{fzf}. Write a command to use \textit{fzf} to select a PDF from the data we gathered above.
\end{enumerate}

\subsubsection{Opening the file using Zathura}
Now that have selected which PDF we want to open, we can use a very minimalistic program called \textit{Zathura} to open it. Write a command that uses the
commands above to open the file using Zathura.
\paragraph{HINT:} This is how Zathura opens files: \texttt{zathura /path/to/file}
\paragraph{HINT:} Learn what the syntax \texttt{zathura \$(\textit{command})} does and use to open the PDF we have selected.

\section{Git and FOSS}
\subsection{README.md}
Make sure to include a basic README.md file in your GitHub repository that describes the aim of this repository and its purpose.

Make sure to use headings and lists in your README.md file.

\subsection{Issues}
Create a sample issue in the repository below and attach its screenshot in your LaTeX document:

\url{https://github.com/MiliAxe/CW-Final}

\subsection{FOSS contribution}
Do you see yourself contributing to FOSS projects in the future? If yes, what kind of projects are you interested in contributing to? If no, why not?


\pagebreak

\section*{Submission Guidelines}
Your final submission should include:
\begin{itemize}
    \item A link to your GitHub repository.
    \item The compiled PDF of your LaTeX document.
    \item All source files used in the creation of the document and scripts.
\end{itemize}

\section*{Evaluation Criteria}
You will be evaluated on the following:
\begin{itemize}
    \item The completeness and quality of your LaTeX document.
    \item The use of Git and GitHub, including commit history and usage of GitHub Actions.
    \item The depth of exploration and learning in each of the tasks.

\item Your ability to follow the submission guidelines accurately.
\end{itemize}

Good luck!

\end{document}